Some Graphical Realizations of Two-Row Specht Modules of Hecke Algebras

### 2019-07-26 tex/Rough-Overview.tex

\begin{titlepage}
  \maketitle
  \begin{abstract}
  Abstract goes here
  \end{abstract}
\end{titlepage}

>>>>

\begin{titlepage}
  \maketitle
  \begin{abstract}
    We are concerned with Specht Modules corresponding to Young diagrams of two rows.
    When the Iwahori-Hecke algebra of the symmetric group has vanishing parameter $e$, for diagram $(n + r,n)$ we first define a \emph{Crossingless Matchings Representation} on $2n + r$ nodes with $r$ anchors $M_{2n + r}^r$, and we use modular branching rules to prove the isomorphism to the corresponding specht module $M_{2n + r}^r \simeq S^{(n+r,n)'}$ in the case that $e > n$ and the specht module is irreducible.
    We additionally give conjecture in the direction of a proof in the general case.
    Next, we adopt the Fibonacci representation $V$ to the Iwahori-Hecke algebra in the case $e = 5$ and characterise the quotients $D^{(n+r,n)}$ with $r \leq 3$ via isomorphism with two subrepresentations based on first and last character;
    additionally, we decompose the other two of these into direct sums of the first two, and thus achieve a graphical realization of $D^{(n+r,n)}$ at $e = 5$, $r\leq 3$ and decompose the fibonacci representation into a direct sum of these quotients of Specht modules.
    Last, some heuristics are presented to support our conjecture and give explicit transitions from $M \rightarrow V$ in cases with small $n$.
  \end{abstract}

\tableofcontents

\end{titlepage}
